---
title: "Final_Project"
output:
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Steps we took to complete project

###ETL ("Clean Up") the Data -
 
```{r ETL,eval = FALSE}
source ("../01 Data/R_ETLWages1.csv")
source ("../01 Data/R_ETLWages2.csv")
```
###Data Description
This data set contains the following fields:
c("id","date","year","industry_format","ticker","name","currency","total_assets","income","employee","total_liabilities","income_tax_paid","operating_expenses","status","market_value","price","city","state")
#str(df) # Uncomment this line and  run just the lines to here to get column types to use for getting the list of measures.

measures <- c("total_assets","income","employee","total_liabilities","income_tax_paid","operating_expenses","market_value","price")
 - id- 
 
 - date-
 
 - year- 
 
 - industry_format
 
 - ticker- 
 
 - name-
 
 - currency
 
 - total_assets
 
 - income
 
 - employe

 - City- city where company is headquartered
 
 - State- State where company is headquartered


###Joining the Data

We joined the data using a inner join to combine states with their respective regions. 


```{}
SELECT Wages1.unique_num,school, wage, exper, sex, marital status, state
        FROM Wages1, `Wages2.csv`
        WHERE Wages1.unique_num = `Wages2.csv`.unique_num
```
###Non-Aggregated Measures Analysis

###Aggregated Measures Analysis

###Scatter Plots

###Crosstabs

###Barcharts


## Shiny
  After we had workable data, we developed a Shiny App. Each tab of the Shiny App displays the equivalent ggplot code that creates the same visualization as Tableau. 
  
If you wish to run the app, it is under 02 Shiny. It is also hosted with this URL. https://chriswongwr.shinyapps.io/project6/

  